% Autogenerated translation of index.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\setmainfont{Helvetica Neue}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}

\hrule
title: 'Monetary and Fiscal Policy Interaction in a Currency Union with Heterogeneous Agents'

\chapter*{Authors}

\chapter*{If you created a profile for a user (e.g. the default \texttt{admin} user), write the username (folder name) here}

\chapter*{and it will be replaced with their full name and linked to their profile.}

authors:
  - admin

\chapter*{Author notes (optional)}

\chapter*{author\_notes:}

\chapter*{- 'Equal contribution'}

\chapter*{- 'Equal contribution'}

date: '2023-11-01T00:00:00Z'
doi: ''

\chapter*{Schedule page publish date (NOT publication's date).}

publishDate: '2017-01-01T00:00:00Z'

\chapter*{Publication type.}

\chapter*{Legend: 0 = Uncategorized; 1 = Conference paper; 2 = Journal article;}

\chapter*{3 = Preprint / Working Paper; 4 = Report; 5 = Book; 6 = Book section;}

\chapter*{7 = Thesis; 8 = Patent}

\chapter*{publication\_types: ['7']}

\chapter*{Publication name and optional abbreviated publication name.}

\chapter*{publication:}

\chapter*{publication\_short: In \emph{ICW}}

abstract: How does household heterogeneity affect the transmission of macroeconomic shocks and the interaction of fiscal and monetary policy in a currency union? This paper develops a two-country New Keynesian model of a currency union with household heterogeneity. Member countries are subject to a union-wide monetary policy, but differ in the degree of households heterogeneity and feature sovereign fiscal authorities with counter-cyclical stabilization objectives. The framework provides novel evidence of changes in the response to shocks, both quantitatively and qualitatively, as well as profound policy implications and spillover effects when household heterogeneity is taken into account. The effects of monetary policy and cost-push shocks are significantly amplified. A union-wide productivity shock results in a pronounced economic boom requiring fiscal and monetary policy contractions. In stark contrast to the representative agents literature, a domestic fiscal policy shock has the effect of crowding in private consumption. The existence of Keynesian households in one country of the currency union also results in profound spillover effects to other countries transmitted through the trade of goods and a terms-of-trade channel. Countries with lower proportions of Keynesian households inherit the amplification caused by hand-to-mouth households in other countries. The magnitude of spillover effects tends to increase with the degree of trade openness of the economies.

\chapter*{Summary. An optional shortened abstract.}

summary: This paper develops a two-country New Keynesian model of a currency union with households heterogeneity. Member countries are subject to a union-wide monetary policy, but differ in the degree of households heterogeneity and feature sovereign fiscal authorities with counter-cyclical stabilization objectives. The framework provides novel evidence of changes in the response to shocks, both quantitatively and qualitatively, as well as profound policy implications and spillover effects when household heterogeneity is taken into account.

tags: []

\chapter*{Display this page in the Featured widget?}

featured: true

\chapter*{Custom links (uncomment lines below)}

\chapter*{links:}

\chapter*{- name: Custom Link}

\chapter*{url: http://example.org}

url\emph{pdf: ''
url}code: ''
url\emph{dataset: ''
url}poster: ''
url\emph{project: ''
url}slides: ''
url\emph{source: ''
url}video: ''

\chapter*{Featured image}

\chapter*{To use, add an image named \texttt{featured.jpg/png} to your page's folder.}

image:
  caption: ''
  focal\emph{point: ''
  preview}only: false

\chapter*{Associated Projects (optional).}

\chapter*{Associate this publication with one or more of your projects.}

\chapter*{Simply enter your project's folder or file name without extension.}

\chapter*{E.g. \texttt{internal-project} references \texttt{content/project/internal-project/index.md}.}

\chapter*{Otherwise, set \texttt{projects: []}.}

projects:
  - example

\chapter*{Slides (optional).}

\chapter*{Associate this publication with Markdown slides.}

\chapter*{Simply enter your slide deck's filename without extension.}

\chapter*{E.g. \texttt{slides: "example"} references \texttt{content/slides/example/index.md}.}

\chapter*{Otherwise, set \texttt{slides: ""}.}

\section*{slides: example}

\end{document}
